Spike-and-Slab Generalized Additive Models and Scalable Algorithms for High-Dimensional Data

### 2022-03-21 Manuscript/Tabs/sim_binom_tab.tex
Edit Captions

\begin{table}[ht]
\centering
\begin{tabular}{cccccccc}
  \hline
P & mgcv & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & 0.94 (0.01) & 0.83 (0.01) & 0.90 (0.01) & 0.90 (0.01) & 0.92 (0.01) & 0.92 (0.01) & 0.90 (0.00) \\ 
   10 & 0.92 (0.03) & 0.83 (0.00) & 0.86 (0.04) & 0.86 (0.03) & 0.92 (0.01) & 0.92 (0.01) & 0.90 (0.00) \\ 
   50 & 0.76 (0.03) & 0.83 (0.01) & 0.83 (0.02) & 0.84 (0.02) & 0.90 (0.01) & 0.92 (0.01) & 0.89 (0.01) \\ 
  100 & NaN (NA) & 0.83 (0.01) & 0.83 (0.02) & 0.81 (0.09) & 0.90 (0.01) & 0.92 (0.01) & 0.88 (0.01) \\ 
  200 & NaN (NA) & 0.83 (0.01) & 0.81 (0.06) & 0.82 (0.05) & 0.88 (0.02) & 0.92 (0.01) & 0.87 (0.02) \\ 
   \hline
\end{tabular}
\caption{The average and standard deviation of the out-of-sample area under the curve measures
    for binomial outcomes over 50 iterations. The models of comparison include the proposed Bayesian
    hierarchical additive model (BHAM) fitted with Iterative Weighted Least Square (BHAM-IWLS) and
    Coordinate Descent (BHAM-CD) algorithms, component selection and smoothing operator (COSSO),
    adaptive COSSO, mgcv and sparse Bayesian generalized additive model (SB-GAM). mgcv doesn't provide
    estimation whe number of parameters exceeds sample size i.e. p = 100, 200.} 
\label{tab:bin_auc}
\end{table}

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{cccccccc}
  \hline
P & mgcv & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & 0.94 (0.01) & 0.83 (0.01) & 0.90 (0.01) & 0.90 (0.01) & 0.92 (0.01) & 0.92 (0.01) & 0.90 (0.00) \\ 
   10 & 0.92 (0.03) & 0.83 (0.00) & 0.86 (0.04) & 0.86 (0.03) & 0.92 (0.01) & 0.92 (0.01) & 0.90 (0.00) \\ 
   50 & 0.76 (0.03) & 0.83 (0.01) & 0.83 (0.02) & 0.84 (0.02) & 0.90 (0.01) & 0.92 (0.01) & 0.89 (0.01) \\ 
  100 & - & 0.83 (0.01) & 0.83 (0.02) & 0.81 (0.09) & 0.90 (0.01) & 0.92 (0.01) & 0.88 (0.01) \\ 
  200 & - & 0.83 (0.01) & 0.81 (0.06) & 0.82 (0.05) & 0.88 (0.02) & 0.92 (0.01) & 0.87 (0.02) \\ 
   \hline
\end{tabular}
\caption{The average and standard deviation of the out-of-sample area under the curve measures
    for binomial outcomes over 50 iterations. The models of comparison include the proposed Bayesian
    hierarchical additive model (BHAM), component selection and smoothing operator (COSSO),
    adaptive COSSO, mgcv and sparse Bayesian generalized additive model (SB-GAM). mgcv doesn't provide
    estimation whe number of parameters exceeds sample size i.e. p = 100, 200.} 
\label{tab:bin_auc}
\end{table}

### 2022-03-21 Manuscript/Tabs/sim_binom_var_slct_tab.tex
Edit Captions

\begin{table}[ht]
\centering
\begin{tabular}{ccccccccc}
  \hline
P & Metric & mgcv & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & Precision & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ 
   10 & Precision & 0.88 & 0.58 & 0.71 & 0.69 & 0.93 & 0.88 & 0.89 \\ 
   50 & Precision &  & 0.38 & 0.60 & 0.59 & 0.77 & 0.80 & 0.52 \\ 
  100 & Precision &  & 0.35 & 0.62 & 0.65 & 0.82 & 0.77 & 0.42 \\ 
  200 & Precision &  & 0.29 & 0.65 & 0.57 & 0.21 & 0.74 & 0.36 \\ 
    4 & Recall & 1.00 & 0.54 & 0.61 & 0.54 & 0.38 & 0.97 & 0.55 \\ 
   10 & Recall & 0.92 & 0.46 & 0.50 & 0.54 & 0.38 & 0.97 & 0.54 \\ 
   50 & Recall & 0.00 & 0.34 & 0.30 & 0.30 & 0.32 & 0.90 & 0.55 \\ 
  100 & Recall &  & 0.27 & 0.30 & 0.25 & 0.27 & 0.92 & 0.54 \\ 
  200 & Recall &  & 0.27 & 0.25 & 0.29 & 0.56 & 0.92 & 0.53 \\ 
    4 & MCC &  &  &  &  &  &  &  \\ 
   10 & MCC & 0.89 & 0.18 & 0.35 & 0.36 & 0.47 & 0.86 & 0.55 \\ 
   50 & MCC &  & 0.25 & 0.34 & 0.36 & 0.45 & 0.83 & 0.47 \\ 
  100 & MCC &  & 0.24 & 0.37 & 0.37 & 0.45 & 0.82 & 0.43 \\ 
  200 & MCC &  & 0.23 & 0.36 & 0.36 & 0.23 & 0.81 & 0.40 \\ 
   \hline
\end{tabular}
\caption{} 
\label{}
\end{table}

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{cccccccc}
  \hline
P & Metric & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & Precision & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ 
   10 & Precision & 0.58 & 0.71 & 0.69 & 0.93 & 0.88 & 0.89 \\ 
   50 & Precision & 0.38 & 0.60 & 0.59 & 0.77 & 0.80 & 0.52 \\ 
  100 & Precision & 0.35 & 0.62 & 0.65 & 0.82 & 0.77 & 0.42 \\ 
  200 & Precision & 0.29 & 0.65 & 0.57 & 0.21 & 0.74 & 0.36 \\ 
    4 & Recall & 0.54 & 0.61 & 0.54 & 0.38 & 0.97 & 0.55 \\ 
   10 & Recall & 0.46 & 0.50 & 0.54 & 0.38 & 0.97 & 0.54 \\ 
   50 & Recall & 0.34 & 0.30 & 0.30 & 0.32 & 0.90 & 0.55 \\ 
  100 & Recall & 0.27 & 0.30 & 0.25 & 0.27 & 0.92 & 0.54 \\ 
  200 & Recall & 0.27 & 0.25 & 0.29 & 0.56 & 0.92 & 0.53 \\ 
   10 & MCC & 0.18 & 0.35 & 0.36 & 0.47 & 0.86 & 0.55 \\ 
   50 & MCC & 0.25 & 0.34 & 0.36 & 0.45 & 0.83 & 0.47 \\ 
  100 & MCC & 0.24 & 0.37 & 0.37 & 0.45 & 0.82 & 0.43 \\ 
  200 & MCC & 0.23 & 0.36 & 0.36 & 0.23 & 0.81 & 0.40 \\ 
   \hline
\end{tabular}
\caption{} 
\label{tab:sim_binom_var_select}
\end{table}

### 2022-03-21 Manuscript/Tabs/sim_gaus_tab.tex
replace mgcv NA values (#23)
Edit Captions

\begin{table}[ht]
\centering
\begin{tabular}{cccccccc}
  \hline
P & mgcv & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & 0.90 (0.01) & 0.33 (0.01) & 0.71 (0.13) & 0.72 (0.11) & 0.90 (0.01) & 0.79 (0.04) & 0.80 (0.00) \\ 
   10 & 0.90 (0.01) & 0.33 (0.01) & 0.66 (0.21) & 0.77 (0.02) & 0.89 (0.01) & 0.79 (0.04) & 0.79 (0.00) \\ 
   50 & 0.86 (0.02) & 0.32 (0.01) & 0.46 (0.19) & 0.57 (0.18) & 0.80 (0.02) & 0.78 (0.05) & 0.78 (0.01) \\ 
  100 & NaN (NA) & 0.32 (0.01) & 0.41 (0.23) & 0.48 (0.25) & 0.79 (0.01) & 0.79 (0.05) & 0.77 (0.01) \\ 
  200 & NaN (NA) & 0.32 (0.01) & 0.39 (0.19) & 0.40 (0.17) & 0.79 (0.01) & 0.78 (0.04) & 0.75 (0.01) \\ 
   \hline
\end{tabular}
\caption{The average and standard deviation of the out-of-sample $R^2$ measure for
    Gaussian outcomes over 50 iterations. The models of comparison include the proposed Bayesian
    hierarchical additive model (BHAM) fitted with Iterative Weighted Least Square (BHAM-IWLS) and
    Coordinate Descent (BHAM-CD) algorithms, component selection and smoothing operator (COSSO), adaptive
    COSSO, mgcv and sparse Bayesian generalized additive model (SB-GAM). mgcv doesn't provide estimation
    whe number of parameters exceeds sample size i.e. p = 100, 200.} 
\label{tab:gaus}
\end{table}

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{cccccccc}
  \hline
P & mgcv & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & 0.90 (0.01) & 0.33 (0.01) & 0.71 (0.13) & 0.72 (0.11) & 0.90 (0.01) & 0.79 (0.04) & 0.80 (0.00) \\ 
   10 & 0.90 (0.01) & 0.33 (0.01) & 0.66 (0.21) & 0.77 (0.02) & 0.89 (0.01) & 0.79 (0.04) & 0.79 (0.00) \\ 
   50 & 0.86 (0.02) & 0.32 (0.01) & 0.46 (0.19) & 0.57 (0.18) & 0.80 (0.02) & 0.78 (0.05) & 0.78 (0.01) \\ 
  100 & - & 0.32 (0.01) & 0.41 (0.23) & 0.48 (0.25) & 0.79 (0.01) & 0.79 (0.05) & 0.77 (0.01) \\ 
  200 & - & 0.32 (0.01) & 0.39 (0.19) & 0.40 (0.17) & 0.79 (0.01) & 0.78 (0.04) & 0.75 (0.01) \\ 
   \hline
\end{tabular}
\caption{The average and standard deviation of the out-of-sample $R^2$ measure for
    Gaussian outcomes over 50 iterations. The models of comparison include the proposed Bayesian
    hierarchical additive model (BHAM), component selection and smoothing operator (COSSO), adaptive
    COSSO, mgcv and sparse Bayesian generalized additive model (SB-GAM). mgcv doesn't provide estimation
    whe number of parameters exceeds sample size i.e. p = 100, 200.} 
\label{tab:gaus}
\end{table}

### 2022-03-21 Manuscript/Tabs/sim_gaus_var_slct_tab.tex
Revise simulaiton results
Revise and add caption to the plot
Edit Captions

\begin{table}[ht]
\centering
\begin{tabular}{ccccccccc}
  \hline
P & Metric & mgcv & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & Precision & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ 
   10 & Precision & 0.89 & 0.76 & 0.84 & 0.93 & 0.62 & 0.86 & 1.00 \\ 
   50 & Precision & 0.36 & 0.48 & 0.70 & 0.69 & 0.88 & 0.75 & 1.00 \\ 
  100 & Precision &  & 0.43 & 0.61 & 0.59 & 0.99 & 0.79 & 0.99 \\ 
  200 & Precision &  & 0.36 & 0.61 & 0.47 & 0.28 & 0.75 & 0.99 \\ 
    4 & Recall & 1.00 & 0.53 & 0.49 & 0.53 & 0.88 & 0.99 & 0.51 \\ 
   10 & Recall & 1.00 & 0.40 & 0.52 & 0.52 & 0.83 & 1.00 & 0.50 \\ 
   50 & Recall & 1.00 & 0.35 & 0.40 & 0.48 & 0.37 & 1.00 & 0.50 \\ 
  100 & Recall &  & 0.33 & 0.36 & 0.40 & 0.30 & 0.99 & 0.50 \\ 
  200 & Recall &  & 0.32 & 0.33 & 0.35 & 0.52 & 1.00 & 0.50 \\ 
    4 & MCC &  &  &  &  &  &  &  \\ 
   10 & MCC & 0.90 & 0.32 & 0.49 & 0.57 & 0.46 & 0.86 & 0.61 \\ 
   50 & MCC & 0.54 & 0.31 & 0.47 & 0.53 & 0.50 & 0.83 & 0.69 \\ 
  100 & MCC &  & 0.32 & 0.41 & 0.45 & 0.53 & 0.87 & 0.70 \\ 
  200 & MCC &  & 0.28 & 0.41 & 0.38 & 0.36 & 0.85 & 0.70 \\ 
   \hline
\end{tabular}
\caption{} 
\label{}
\end{table}

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{cccccccc}
  \hline
P & Metric & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & Precision & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ 
   10 & Precision & 0.76 & 0.84 & 0.93 & 0.62 & 0.86 & 1.00 \\ 
   50 & Precision & 0.48 & 0.70 & 0.69 & 0.88 & 0.75 & 1.00 \\ 
  100 & Precision & 0.43 & 0.61 & 0.59 & 0.99 & 0.79 & 0.99 \\ 
  200 & Precision & 0.36 & 0.61 & 0.47 & 0.28 & 0.75 & 0.99 \\ 
    4 & Recall & 0.53 & 0.49 & 0.53 & 0.88 & 0.99 & 0.51 \\ 
   10 & Recall & 0.40 & 0.52 & 0.52 & 0.83 & 1.00 & 0.50 \\ 
   50 & Recall & 0.35 & 0.40 & 0.48 & 0.37 & 1.00 & 0.50 \\ 
  100 & Recall & 0.33 & 0.36 & 0.40 & 0.30 & 0.99 & 0.50 \\ 
  200 & Recall & 0.32 & 0.33 & 0.35 & 0.52 & 1.00 & 0.50 \\ 
   10 & MCC & 0.32 & 0.49 & 0.57 & 0.46 & 0.86 & 0.61 \\ 
   50 & MCC & 0.31 & 0.47 & 0.53 & 0.50 & 0.83 & 0.69 \\ 
  100 & MCC & 0.32 & 0.41 & 0.45 & 0.53 & 0.87 & 0.70 \\ 
  200 & MCC & 0.28 & 0.41 & 0.38 & 0.36 & 0.85 & 0.70 \\ 
   \hline
\end{tabular}
\caption{} 
\label{tab:sim_gaus_var_select}
\end{table}

### 2022-03-21 Manuscript/Tabs/sim_lnr_binom_tab.tex
Organize prediction Table to latex output (#23)
replace mgcv NA values (#23)
Edit Captions

\begin{table}[ht]
\centering
\begin{tabular}{cccccccc}
  \hline
P & mgcv & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & 0.94 (0.01) & 0.83 (0.01) & 0.90 (0.01) & 0.90 (0.01) & 0.92 (0.01) & 0.92 (0.01) & 0.90 (0.00) \\ 
   10 & 0.92 (0.03) & 0.83 (0.00) & 0.86 (0.04) & 0.86 (0.03) & 0.92 (0.01) & 0.92 (0.01) & 0.90 (0.00) \\ 
   50 & 0.76 (0.03) & 0.83 (0.01) & 0.83 (0.02) & 0.84 (0.02) & 0.90 (0.01) & 0.92 (0.01) & 0.89 (0.01) \\ 
  100 & NaN (NA) & 0.83 (0.01) & 0.83 (0.02) & 0.81 (0.09) & 0.90 (0.01) & 0.92 (0.01) & 0.88 (0.01) \\ 
  200 & NaN (NA) & 0.83 (0.01) & 0.81 (0.06) & 0.82 (0.05) & 0.88 (0.02) & 0.92 (0.01) & 0.87 (0.02) \\ 
   \hline
\end{tabular}
\caption{The average and standard deviation of the out-of-sample area under the curve measures
    for binomial outcomes over 50 iterations. The models of comparison include the proposed Bayesian
    hierarchical additive model (BHAM) fitted with Iterative Weighted Least Square (BHAM-IWLS) and
    Coordinate Descent (BHAM-CD) algorithms, component selection and smoothing operator (COSSO),
    adaptive COSSO, mgcv and sparse Bayesian generalized additive model (SB-GAM). mgcv doesn't provide
    estimation whe number of parameters exceeds sample size i.e. p = 100, 200.} 
\label{tab:bin_auc}
\end{table}

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{cccccccc}
  \hline
P & mgcv & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & 0.79 (0.01) & 0.79 (0.01) & 0.76 (0.04) & 0.75 (0.04) & 0.78 (0.01) & 0.76 (0.01) & 0.79 (0.01) \\ 
   10 & 0.77 (0.01) & 0.79 (0.01) & 0.78 (0.01) & 0.78 (0.01) & 0.78 (0.01) & 0.75 (0.01) & 0.79 (0.01) \\ 
   50 & 0.62 (0.01) & 0.78 (0.01) & 0.75 (0.03) & 0.73 (0.04) & 0.74 (0.07) & 0.75 (0.02) & 0.77 (0.01) \\ 
  100 & - & 0.78 (0.01) & 0.73 (0.04) & 0.69 (0.05) & 0.73 (0.07) & 0.74 (0.02) & 0.76 (0.02) \\ 
  200 & - & 0.78 (0.01) & 0.71 (0.05) & 0.67 (0.05) & 0.73 (0.06) & 0.73 (0.03) & 0.72 (0.03) \\ 
   \hline
\end{tabular}
\caption{The average and standard deviation of the out-of-sample area under the curve measures
    for binomial outcomes over 50 iterations. The models of comparison include the proposed Bayesian
    hierarchical additive model (BHAM), component selection and smoothing operator (COSSO),
    adaptive COSSO, mgcv and sparse Bayesian generalized additive model (SB-GAM). mgcv doesn't provide
    estimation whe number of parameters exceeds sample size i.e. p = 100, 200.} 
\label{tab:lnr_bin_auc}
\end{table}

### 2022-03-21 Manuscript/Tabs/sim_lnr_binom_var_slct_tab.tex
Edit Captions

\begin{table}[ht]
\centering
\begin{tabular}{ccccccccc}
  \hline
P & Metric & mgcv & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & Precision & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ 
   10 & Precision & 0.94 & 0.61 & 0.97 & 0.98 & 0.55 & 0.74 & 0.91 \\ 
   50 & Precision &  & 0.35 & 0.59 & 0.68 & 0.26 & 0.59 & 0.61 \\ 
  100 & Precision &  & 0.28 & 0.47 & 0.51 & 0.30 & 0.46 & 0.57 \\ 
  200 & Precision &  & 0.26 & 0.44 & 0.42 & 0.38 & 0.41 & 0.38 \\ 
    4 & Recall & 1.00 & 1.00 & 0.85 & 0.78 & 1.00 & 1.00 & 1.00 \\ 
   10 & Recall & 1.00 & 1.00 & 0.96 & 0.97 & 0.99 & 1.00 & 1.00 \\ 
   50 & Recall & 0.00 & 1.00 & 0.88 & 0.74 & 0.92 & 1.00 & 1.00 \\ 
  100 & Recall &  & 1.00 & 0.78 & 0.56 & 0.89 & 1.00 & 0.99 \\ 
  200 & Recall &  & 1.00 & 0.67 & 0.48 & 0.89 & 0.99 & 0.98 \\ 
    4 & MCC &  &  &  &  &  &  &  \\ 
   10 & MCC & 0.94 & 0.58 & 0.95 & 0.96 & 0.49 & 0.72 & 0.91 \\ 
   50 & MCC &  & 0.52 & 0.66 & 0.65 & 0.37 & 0.73 & 0.74 \\ 
  100 & MCC &  & 0.49 & 0.55 & 0.47 & 0.43 & 0.65 & 0.72 \\ 
  200 & MCC &  & 0.49 & 0.49 & 0.39 & 0.47 & 0.62 & 0.58 \\ 
   \hline
\end{tabular}
\caption{} 
\label{}
\end{table}

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{cccccccc}
  \hline
P & Metric & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & Precision & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ 
   10 & Precision & 0.61 & 0.97 & 0.98 & 0.55 & 0.74 & 0.91 \\ 
   50 & Precision & 0.35 & 0.59 & 0.68 & 0.26 & 0.59 & 0.61 \\ 
  100 & Precision & 0.28 & 0.47 & 0.51 & 0.30 & 0.46 & 0.57 \\ 
  200 & Precision & 0.26 & 0.44 & 0.42 & 0.38 & 0.41 & 0.38 \\ 
    4 & Recall & 1.00 & 0.85 & 0.78 & 1.00 & 1.00 & 1.00 \\ 
   10 & Recall & 1.00 & 0.96 & 0.97 & 0.99 & 1.00 & 1.00 \\ 
   50 & Recall & 1.00 & 0.88 & 0.74 & 0.92 & 1.00 & 1.00 \\ 
  100 & Recall & 1.00 & 0.78 & 0.56 & 0.89 & 1.00 & 0.99 \\ 
  200 & Recall & 1.00 & 0.67 & 0.48 & 0.89 & 0.99 & 0.98 \\ 
   10 & MCC & 0.58 & 0.95 & 0.96 & 0.49 & 0.72 & 0.91 \\ 
   50 & MCC & 0.52 & 0.66 & 0.65 & 0.37 & 0.73 & 0.74 \\ 
  100 & MCC & 0.49 & 0.55 & 0.47 & 0.43 & 0.65 & 0.72 \\ 
  200 & MCC & 0.49 & 0.49 & 0.39 & 0.47 & 0.62 & 0.58 \\ 
   \hline
\end{tabular}
\caption{} 
\label{tab:sim_lnr_binom_var_select}
\end{table}

### 2022-03-21 Manuscript/Tabs/sim_lnr_gaus_tab.tex
Organize prediction Table to latex output (#23)
Edit Captions

\begin{table}[ht]
\centering
\begin{tabular}{cccccccc}
  \hline
P & mgcv & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & 0.90 (0.01) & 0.33 (0.01) & 0.71 (0.13) & 0.72 (0.11) & 0.90 (0.01) & 0.79 (0.04) & 0.80 (0.00) \\ 
   10 & 0.90 (0.01) & 0.33 (0.01) & 0.66 (0.21) & 0.77 (0.02) & 0.89 (0.01) & 0.79 (0.04) & 0.79 (0.00) \\ 
   50 & 0.86 (0.02) & 0.32 (0.01) & 0.46 (0.19) & 0.57 (0.18) & 0.80 (0.02) & 0.78 (0.05) & 0.78 (0.01) \\ 
  100 & NaN (NA) & 0.32 (0.01) & 0.41 (0.23) & 0.48 (0.25) & 0.79 (0.01) & 0.79 (0.05) & 0.77 (0.01) \\ 
  200 & NaN (NA) & 0.32 (0.01) & 0.39 (0.19) & 0.40 (0.17) & 0.79 (0.01) & 0.78 (0.04) & 0.75 (0.01) \\ 
   \hline
\end{tabular}
\caption{The average and standard deviation of the out-of-sample $R^2$ measure for
    Gaussian outcomes over 50 iterations. The models of comparison include the proposed Bayesian
    hierarchical additive model (BHAM) fitted with Iterative Weighted Least Square (BHAM-IWLS) and
    Coordinate Descent (BHAM-CD) algorithms, component selection and smoothing operator (COSSO), adaptive
    COSSO, mgcv and sparse Bayesian generalized additive model (SB-GAM). mgcv doesn't provide estimation
    whe number of parameters exceeds sample size i.e. p = 100, 200.} 
\label{tab:gaus}
\end{table}

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{cccccccc}
  \hline
P & mgcv & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & 0.38 (0.01) & 0.39 (0.01) & 0.31 (0.08) & 0.29 (0.11) & 0.38 (0.01) & 0.35 (0.01) & 0.39 (0.01) \\ 
   10 & 0.36 (0.02) & 0.38 (0.01) & 0.35 (0.03) & 0.34 (0.04) & 0.39 (0.01) & 0.33 (0.02) & 0.39 (0.01) \\ 
   50 & 0.09 (0.09) & 0.37 (0.01) & 0.30 (0.06) & 0.30 (0.36) & 0.38 (0.01) & 0.32 (0.03) & 0.37 (0.01) \\ 
  100 & - & 0.37 (0.01) & 0.28 (0.07) & 0.34 (0.04) & 0.38 (0.01) & 0.29 (0.07) & 0.35 (0.01) \\ 
  200 & - & 0.36 (0.01) & 0.26 (0.08) & 0.31 (0.06) & 0.38 (0.03) & 0.28 (0.06) & 0.33 (0.02) \\ 
   \hline
\end{tabular}
\caption{The average and standard deviation of the out-of-sample $R^2$ measure for
    Gaussian outcomes over 50 iterations. The models of comparison include the proposed Bayesian
    hierarchical additive model (BHAM), component selection and smoothing operator (COSSO), adaptive
    COSSO, mgcv and sparse Bayesian generalized additive model (SB-GAM). mgcv doesn't provide estimation
    whe number of parameters exceeds sample size i.e. p = 100, 200.} 
\label{tab:lnr_gaus}
\end{table}

### 2022-03-21 Manuscript/Tabs/sim_lnr_gaus_var_slct_tab.tex
Edit Captions

\begin{table}[ht]
\centering
\begin{tabular}{ccccccccc}
  \hline
P & Metric & mgcv & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & Precision & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ 
   10 & Precision & 0.91 & 0.59 & 0.97 & 0.97 & 0.90 & 0.56 & 0.99 \\ 
   50 & Precision & 0.39 & 0.43 & 0.74 & 0.84 & 0.89 & 0.39 & 0.99 \\ 
  100 & Precision &  & 0.34 & 0.53 & 0.72 & 0.91 & 0.29 & 0.99 \\ 
  200 & Precision &  & 0.27 & 0.42 & 0.52 & 0.92 & 0.33 & 0.99 \\ 
    4 & Recall & 1.00 & 1.00 & 0.87 & 0.84 & 1.00 & 1.00 & 1.00 \\ 
   10 & Recall & 1.00 & 1.00 & 0.98 & 0.96 & 1.00 & 1.00 & 1.00 \\ 
   50 & Recall & 1.00 & 1.00 & 0.85 & 0.99 & 1.00 & 1.00 & 1.00 \\ 
  100 & Recall &  & 1.00 & 0.84 & 0.97 & 1.00 & 1.00 & 1.00 \\ 
  200 & Recall &  & 1.00 & 0.78 & 0.88 & 1.00 & 0.98 & 1.00 \\ 
    4 & MCC &  &  &  &  &  &  &  \\ 
   10 & MCC & 0.91 & 0.59 & 0.96 & 0.94 & 0.91 & 0.54 & 0.99 \\ 
   50 & MCC & 0.57 & 0.59 & 0.76 & 0.90 & 0.92 & 0.57 & 1.00 \\ 
  100 & MCC &  & 0.54 & 0.61 & 0.81 & 0.94 & 0.48 & 1.00 \\ 
  200 & MCC &  & 0.49 & 0.52 & 0.64 & 0.95 & 0.52 & 0.99 \\ 
   \hline
\end{tabular}
\caption{} 
\label{}
\end{table}

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{cccccccc}
  \hline
P & Metric & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & Precision & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ 
   10 & Precision & 0.59 & 0.97 & 0.97 & 0.90 & 0.56 & 0.99 \\ 
   50 & Precision & 0.43 & 0.74 & 0.84 & 0.89 & 0.39 & 0.99 \\ 
  100 & Precision & 0.34 & 0.53 & 0.72 & 0.91 & 0.29 & 0.99 \\ 
  200 & Precision & 0.27 & 0.42 & 0.52 & 0.92 & 0.33 & 0.99 \\ 
    4 & Recall & 1.00 & 0.87 & 0.84 & 1.00 & 1.00 & 1.00 \\ 
   10 & Recall & 1.00 & 0.98 & 0.96 & 1.00 & 1.00 & 1.00 \\ 
   50 & Recall & 1.00 & 0.85 & 0.99 & 1.00 & 1.00 & 1.00 \\ 
  100 & Recall & 1.00 & 0.84 & 0.97 & 1.00 & 1.00 & 1.00 \\ 
  200 & Recall & 1.00 & 0.78 & 0.88 & 1.00 & 0.98 & 1.00 \\ 
   10 & MCC & 0.59 & 0.96 & 0.94 & 0.91 & 0.54 & 0.99 \\ 
   50 & MCC & 0.59 & 0.76 & 0.90 & 0.92 & 0.57 & 1.00 \\ 
  100 & MCC & 0.54 & 0.61 & 0.81 & 0.94 & 0.48 & 1.00 \\ 
  200 & MCC & 0.49 & 0.52 & 0.64 & 0.95 & 0.52 & 0.99 \\ 
   \hline
\end{tabular}
\caption{} 
\label{tab:sim_lnr_gaus_var_select}
\end{table}
